### 2015-05-16 ase-2015-tex/approach.tex
more global path constraint -> path condition

For field-write in~\figref{fig:fHeap}, after the non-null check and
strengthening of the global heap constraint, it computes the current
references associated with the field in every location in
$\Psi_\cfgnt{x}$. Note that the reference $\cfgnt{r}_x$ is the base
reference whose field, $\cfgnt{r}_\mathit{cur}$ is being written to,
while the reference $r$ is the target reference. The set $\Psi_x$
contains tuples $(\phi\ l\ \cfgnt{r}_\mathit{cur})$ of constraints,
locations, and references. These tuples represent access chains
leading from $\cfgnt{r}_x$ to the reference of the field,
$\cfgnt{r}_\mathit{cur}$. The goal is to change the fields to no
longer point to $\cfgnt{r}_\mathit{cur}$, but rather fresh references
that have both the original locations before the write and the
locations from the write in the value sets (i.e., conditional
write). Since the target of the write is $r$, the rule checks that the
location constraint pairs of $\cfgnt{L}(\cfgnt{r})$ are satisfiable
when accessed through the $\cfgnt{r}_x$ chain in the strengthening
function.  \input{st-def} Constraints on locations are strengthened
with new aliasing conditions and those that are feasible with the
current path constraint are retained.

@@

The rewrite rule to compare two references in the symbolic heap is
shown in~\figref{fig:eqs}. The equals references-true rewrite rule
returns true when two references $\cfgnt{r}_0$ and $\cfgnt{r}_1$
\emph{can} be equal. Intutively, $\Phi_\alpha$ contains all
constraints under which $\cfgnt{r}_0$ and $\cfgnt{r}_1$ may point to
the same location in the symbolic heap. The second set, $\Phi_0$,
contains constraints under which the reference $\cfgnt{r}_0$ points to
corresponding locations such that the reference $\cfgnt{r}_1$
\emph{does not} point to those locations under any
constraint. Finally, the set, $\Phi_1$, contains constraints under
which $\cfgnt{r}_1$ points to corresponding locations and
$\cfgnt{r}_0$ \emph{does not} point to those locations under any
constraint. We use the three sets of constraints to update the current
global heap constraint $\phi_g$ and create a new global heap
constraint $\phi_g^\prime$. We add to $\phi_g$ the disjunction of the
constraints in $\Phi_\alpha$ to indicate that if any of the
constraints are satisfiable, then references $\cfgnt{r}_0$ and
$\cfgnt{r}_1$ can be equal. Furthermore, we conjoin to the global heap
constraint $\phi_g^\prime$, the conjunctions of negations to the
constraints in $\Phi_0$ and $\Phi_1$. This indicates for locations
that are not common to the references, the negations of their
constraints are satisfiable. The rule does not complete (i.e., is not
feasible) if the new global constraint is not satisfied on any
aliasing assignment. In such a case, the $\cfgt{true}$ outcome is not
possible on any symbolic heap. Before the rewrite rule returns
$\cfgt{true}$ we check the satisfiability of the updated global heap
constraint. The reference-false is the logical dual of the rule.

>>>>

For field-write in~\figref{fig:fHeap}, after the non-null check and
strengthening of the global heap constraint, it computes the current
references associated with the field in every location in
$\Psi_\cfgnt{x}$. Note that the reference $\cfgnt{r}_x$ is the base
reference whose field, $\cfgnt{r}_\mathit{cur}$ is being written to,
while the reference $r$ is the target reference. The set $\Psi_x$
contains tuples $(\phi\ l\ \cfgnt{r}_\mathit{cur})$ of constraints,
locations, and references. These tuples represent access chains
leading from $\cfgnt{r}_x$ to the reference of the field,
$\cfgnt{r}_\mathit{cur}$. The goal is to change the fields to no
longer point to $\cfgnt{r}_\mathit{cur}$, but rather fresh references
that have both the original locations before the write and the
locations from the write in the value sets (i.e., conditional
write). Since the target of the write is $r$, the rule checks that the
location constraint pairs of $\cfgnt{L}(\cfgnt{r})$ are satisfiable
when accessed through the $\cfgnt{r}_x$ chain in the strengthening
function.  \input{st-def} Constraints on locations are strengthened
with new aliasing conditions and those that are feasible with the
current path condition are retained.

@@

The rewrite rule to compare two references in the symbolic heap is
shown in~\figref{fig:eqs}. The equals references-true rewrite rule
returns true when two references $\cfgnt{r}_0$ and $\cfgnt{r}_1$
\emph{can} be equal. Intutively, $\Phi_\alpha$ contains all
constraints under which $\cfgnt{r}_0$ and $\cfgnt{r}_1$ may point to
the same location in the symbolic heap. The second set, $\Phi_0$,
contains constraints under which the reference $\cfgnt{r}_0$ points to
corresponding locations such that the reference $\cfgnt{r}_1$
\emph{does not} point to those locations under any
constraint. Finally, the set, $\Phi_1$, contains constraints under
which $\cfgnt{r}_1$ points to corresponding locations and
$\cfgnt{r}_0$ \emph{does not} point to those locations under any
constraint. We use the three sets of constraints to create a new path condition \phi_g^\prime$
as an update of the current path condition $\phi_g$. We add to $\phi_g$ the disjunction of the
constraints in $\Phi_\alpha$ to indicate that if any of the
constraints are satisfiable, then references $\cfgnt{r}_0$ and
$\cfgnt{r}_1$ can be equal. Furthermore, we conjoin to the global heap
constraint $\phi_g^\prime$, the conjunctions of negations to the
constraints in $\Phi_0$ and $\Phi_1$. This indicates for locations
that are not common to the references, the negations of their
constraints are satisfiable. The rule does not complete (i.e., is not
feasible) if the new global constraint is not satisfied on any
aliasing assignment. In such a case, the $\cfgt{true}$ outcome is not
possible on any symbolic heap. Before the rewrite rule returns
$\cfgt{true}$ we check the satisfiability of the updated global heap
constraint. The reference-false is the logical dual of the rule.
